Inferring the effective start dates of non-pharmaceutical interventions during \covid outbreaks

### 2021-09-05 ms/ms.tex
added free to name of ppc free files for submission

        \includegraphics[width=\textwidth]{../figures/ppc/free/Austria_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Belgium_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Denmark_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/France_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Germany_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Italy_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Norway_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Spain_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Sweden_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Switzerland_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/United_Kingdom_ppc_long.pdf}

>>>>

        \includegraphics[width=\textwidth]{../figures/ppc/free/free_Austria_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/free_Belgium_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/free_Denmark_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/free_France_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/free_Germany_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/free_Italy_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/free_Norway_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/free_Spain_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/free_Sweden_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/free_Switzerland_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/free_United_Kingdom_ppc_long.pdf}
